%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{4.08003pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\linespread{1.5}
}{
    \par\kern\topsep
} % new environment for the header


% save the original href command in a new command:
\let\hrefWithoutArrow\href

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%-----------Name-----------
\begin{header}
    \newcommand{\AND}{\unskip
        \cleaders\copy\ANDbox\hskip\wd\ANDbox
        \ignorespaces
    }
    \newsavebox\ANDbox
    \sbox\ANDbox{$|$}

    \fontsize{25 pt}{25 pt}\selectfont İ. Çağkan Çağlayanel

    \vspace{5 pt}

    \normalsize
    \mbox{Ankara, Turkey}%
    \kern 5.0 pt%
    \AND%
    \kern 5.0 pt%
    \mbox{\hrefWithoutArrow{mailto:cagkancaglayanel@gmail.com}{cagkancaglayanel@gmail.com}}%
    \kern 5.0 pt%
    \AND%
    \kern 5.0 pt%
    \mbox{\hrefWithoutArrow{tel:+90-535-671-39-92}{+90 535 671 39 92}}%

    \mbox{\hrefWithoutArrow{https://crosline.github.io/}{crosline.github.io}}%
    \kern 5.0 pt%
    \AND%
    \kern 5.0 pt%
    \mbox{\hrefWithoutArrow{https://linkedin.com/in/crosline}{linkedin.com/in/crosline}}%
    \kern 5.0 pt%
    \AND%
    \kern 5.0 pt%
    \mbox{\hrefWithoutArrow{https://github.com/crosline}{github.com/crosline}}%
\end{header}


%-----------Experience-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Panteon Games}{Feb. 2022 -- Present}
      {Mid-Core Software Engineer}{Nov. 2023 | Ankara, Turkey}
      \resumeItemListStart
        \resumeItem{Created a CI/CD and SCM Pipeline helper solution that coordinates multi-repository testing and automated merge processes across more than 5 Unity and Server projects from a ReactJS web interface. That can run tests on built application on more than 10 devices simultaneously with balanced processing power.}
        \resumeItem{Set Up automated integrations between Project Management Software, Communication and SCM systems (GitLab, Linear, Jira, Jenkins, Discord, Slack) to increase productivity between Design, Backend, Client and Test teams with a custom software.}
        \resumeItem{Helped to develop a comprehensive log tracking and debugging system that acts as a crashlytics service, featuring real time log collection, remote console and debugging abilities without memory overhead.}
        \resumeItem{Containerized the backend ecosystem to improve development workflow of the developers.}
        \resumeItem{Optimized Unity Build Pipeline with a new and easier approach that allows other developers to add new build steps with more than 80\% decreased build times.}
        \resumeItem{Supported and implemented multiple game systems and native optimizations as well as data oriented conversions of performance-critical systems in Unity.}
      \resumeItemListEnd

      \resumeSubSubheading
      {Software Engineer}{Ankara, Turkey}
      \resumeItemListStart
        \resumeItem{Engineered and maintained in-house runtime analytics, ad tracking, monetization by Purchasing and Ad SDKs and remote config solutions for Unity, C\# with increased monetization by 30\%.}
        \resumeItem{Designed tools to improve work efficiency in Unity engine and a Package Manager for easier access and to keep track of the tools in a neat interface.}
        \resumeItem{Led maintenance of 8-10 older HyperCasual/Casual Unity games with regular SDK updates, resolving gameplay issues and bugs while optimizing performance to keep active user retention and revenue streams.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Epic Frame Animation and Production}{Nov. 2021 -- Dec. 2021}
      {Animation Engineering Intern}{Istanbul, Turkey}
      \resumeItemListStart
        \resumeItem{Worked on MoCap data to create procedurally generated animations. Learned to create 3D Models and implement Sprite Animations on Unity.}
        \resumeItem{Made new VFXs and Shaders that acts according to the Physics World.}
        \resumeItem{Created custom scripts in Python for seamless integration between Blender and Unity.}
    \resumeItemListEnd
      
    \resumeSubheading
      {DefTR Technology}{Jun. 2021 -- Nov. 2021}
      {Software \& Test Engineering Intern}{Ankara, Turkey}
      \resumeItemListStart
        \resumeItem{Prototyped a drone, enhanced radio control and ground control softwares. Developed on open-source pathfinding algorithms. Practiced data communication and networking.}
        \resumeItem{Worked on a hardware level, installing sensors, soldering electronic components. Finally tested the safety and reliability of the sensors and the software written. Documented every test and possible outcomes.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hacettepe University}{Sep. 2017 -- Jun 2023}
      {Bachelor of Science, Computer Engineering | GPA 3.00}{Ankara, Turkey}
      \resumeItemListStart
        \resumeItem{Developed a TUBITAK VR Simulation Project in Unity designed to increase recovery speeds of patients with Kinesiophobia as the sole developer within the Computer Graphics Laboratory.}
        \resumeItem{Actively participated in different student organizations. Served as the Chairman of the Manga and Anime Student Club, organizing activities such as drawing, translation, and self-defense. Additionally, founded the Thunderbirds Muggle Quidditch team.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------Courses-----------
\section{Classes}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \vspace{1mm}
     \textbf{Courses}{: Computer Graphics, Game Technologies, Networking, Blockchain, Statistics, Physics, Linear Algebra}

    }}
 \end{itemize}


%-----------Activities-----------
\section{Activity}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arcadia Fansub}{Sep. 2015 -- Current}
      {Co-Founder}{Ankara, Turkey}
      \resumeItemListStart
        \resumeItem{Translation crew with more than 20 members that provides fast and reliable localizations between English, Japanese and Turkish.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Gamejam Participation}{Aug. 2020 -- Current}
      {Co-Founder}{Ankara, Turkey}
      \resumeItemListStart
        \resumeItem{Attended and placed in top 10 in more than 5 Gamejams, most of them had more than 500 submissions. (Brackeys Game Jam, MagaraJam...)}
        \resumeItem{Mentored in large organizations of gamejams with high attendance. (Global Game Jam 24' - 25', HuJam 23')}
      \resumeItemListEnd
      
    \resumeSubheading
      {Conventions}{Sep. 2017 -- Current}
      {Organization Team}{Ankara, Turkey}
      \resumeItemListStart
        \resumeItem{Organizing and working in high attendance (6.000) conventions anime-manga contests, tabletop rpgs, board games and e-sport activities. Worked with a team of 100, joined as a staff member in 2017 and has been the lead of the team since 2019. (HUCON 17' - 18' - 19' - 20' - 21')}
        \resumeItem{Led a team in charge of network systems and streaming services. (DevFest 17' - 18')}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

  
%-----------Projects-----------
\section{Mentionable Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AT0S}{Nov. 2021}
      {Gameplay Developer}{Gamejam}
      \resumeItemListStart
        \resumeItem{Game demo made for MagaraJam\#3 in 72 hours with the theme "System Error". We tell a story that takes place at the future and our character tries to figure an ancient machine with a very glitchy operating system and get the secret documents out of it. It includes some nostalgic titles like the snake. We placed 2nd between 600 other games and 5000 other participants.}
      \resumeItemListEnd
      
    \resumeSubheading
      {VAGABOND}{Apr. 2022}
      {Gameplay Developer}{Gamejam}
      \resumeItemListStart
        \resumeItem{Strategical cutting game demo made for MagaraJam\#4 with similar mechanics to a popular game Fruit Ninja but it may require players to sometimes think outside the box. It includes boss fights and gameplay twists. We ranked 4th between 500 other games.}
      \resumeItemListEnd
      
    \resumeSubheading
      {The Last Session}{Nov. 2022}
      {AI Developer}{Gamejam}
      \resumeItemListStart
        \resumeItem{Tabletop RPG, Dungeons and Dragons inspired game where you are the Game Master that tries to stop the players. Ranked 6th in the gamejam MagaraJam\#5}
      \resumeItemListEnd
      
    \resumeSubheading
      {Beat Menace}{Dec. 2023}
      {AI \& VFX Developer}{Gamejam}
      \resumeItemListStart
        \resumeItem{Hack\&Slash Action game that relies on the music rythims where players can act only if they're following the correct rythm.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------Skill and Interests-----------
\section{Skills \& Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \vspace{1mm}
     \textbf{Programming Languages}{: C\#, Python, Bash, TypeScript (JavaScript), C++, C, SQL, Dart, Java} \\
     \textbf{Game Development}{: Unity, Godot, WebGL} \\
     \textbf{Frontend}{: Flutter, React, Three.js} \\
     \textbf{Backend}{: Asp.NET Core, Entity Framework, Node.js} \\
     \textbf{Version Control}{: Git, Perforce} \\
     \textbf{Design Tools}{: Asp.NET Core, Entity Framework, Node.js} \\
     \textbf{Database}{: SQLite, PostgreSQL, MongoDB} \\
     \textbf{Graphics}{: Shader Graph, OpenCV, HLSL} \\
     \textbf{Project Management}{: Jira, Linear, Trello} \\
     \textbf{DevOps}{: Jenkins, Gitlab CI, Docker, Portainer, Synology, GCP, AWS, Firebase} \\
     \textbf{Languages}{: English (Professional Proficiency), German (Goethe-Zertifikat A2), Turkish (Native)} \\
     \vspace{1mm}
     \textbf{Summary}{: SDK Integration and Development, Build Pipeline Optimization, Real Time Systems, Automation Systems and Cross Platform Development, Game Design Patterns, Memory and CPU Optimizations, Data-Oriented Design, Object Oriented Design} \\
     \vspace{1mm}

    }}
 \end{itemize}

\end{document}